Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-06-02 aosd13/paperBody.tex
Revisions

To make changes to the optimizer more practical, we designed our query
representation so that optimizations are easy to express; restricting to pure
queries also helps. For instance, filter fusion can be implemented simply as:%
\footnote{\code{Sym} nodes are part of the boilerplate we omitted earlier.}
\begin{lstlisting}
  val mergeFilters = ExpTransformer {
    case Sym(Filter(Sym(Filter(collection, pred2)), pred1)) =>
      coll.filter(x => pred2(x) && pred1(x))
  }
\end{lstlisting}
The above code matches on reified expression of form
\code{coll.} \code{filter(pred2).filter(pred1)} and rewrites it. A more complex
optimization such as filter hoisting requires only 20 lines of code.

>>>>

To make changes to the optimizer more practical, we designed our query
representation so that optimizations are easy to express; restricting to pure
queries also helps. For instance, filter fusion can be implemented in few lines of code:
just match against expressions of form \code{coll.filter(pred2).filter(pred1)}
and rewrite them:%
\footnote{\code{Sym} nodes are part of the boilerplate we omitted earlier.}
\begin{lstlisting}
  val mergeFilters = ExpTransformer {
    case Sym(Filter(Sym(Filter(collection, pred2)), pred1)) =>
      coll.filter(x => pred2(x) && pred1(x))
  }
\end{lstlisting}
A more complex
optimization such as filter hoisting requires only 20 lines of code.
